---
title: "ES150A-B"
author: "Shinsuke Adachi"
date: "6/27/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
library(ltm)
library(irtoys)
library(tidyverse)
library(gt)
library(kableExtra)
library(ggplot2)
library(readxl)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.kable.NA = '')
```

### ES150 2020 Term A Grammar
```{r echo=FALSE}
A2020 <- read.csv("2020-ES150-A.csv",header = TRUE)
answersA2020 <- subset(A2020, select = c(33:52, 68:82))
```

## Cleaning
```{r echo=FALSE}
for (col in colnames(answersA2020)){
  answersA2020[[col]][answersA2020[col] =="-"] <- NA
  answersA2020[[col]][answersA2020[col] > 0] <- 1
  answersA2020[[col]] <- as.numeric(answersA2020[[col]])
}
answersA2020 <- rename_with(answersA2020, ~ stringr::str_remove(., "..1.00"))
answersA2020 <- rename_with(answersA2020, ~ stringr::str_remove(., "Q.."))
```



#### EDA

<details>
<summary></summary>

#Boxplot
```{r echo=FALSE}
A2020$Grade_EA[A2020$Grade_EA == 0] <- NA
score <- na.omit(A2020$Grade_EA)
summary(score)
ggplot(A2020, aes(x = Grade_EA)) + geom_boxplot() + ggtitle("ES150 2020 Term A Grammar")
```

#Score distribution
```{r echo=FALSE}

ggplot(A2020, aes(x = Grade_EA)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2020 Term A Grammar")
```

# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(c(23:42, 58:72))

avgData <- vector('numeric', 35L)
for (j in 1:35) avgData[j] <- sum(na.omit(answersA2020[,j]))/length(na.omit(answersA2020[,j]))

testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=10), legend.position = "none", plot.title = element_text(size=10)) + ggtitle("ES150 2020 Term A Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>


#### 2PLM

```{r echo=FALSE}
u_A2020 <- na.omit(answersA2020)
ip_A2020 <- est(resp=u_A2020, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_A2020$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```



#### Difficulty / Dscriminatory Power {.tabset .tabset-fade}

##### List

<details>
<summary></summary>
```{r}
ip_A2020$est
```
V1: discrimination parameter
V2: difficulty parameter

</details>

##### Plot
```{r echo=FALSE}
par(mar = c(4, 4, 2, 2))
plot(ip_A2020$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity", main = "ES150 2020 Term A Grammar", cex.lab = 0.75, cex.axis = 0.75, cex.main = 0.75)
text(ip_A2020$est[,1], ip_A2020$est[,2], paste(rownames(ip_A2020$est)), cex = 0.5)
abline(v = 1, h = 0, lty = 2, lwd = 0.5)
```

## Removing outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_A2020$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_A2020$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_A2020$est[,1] > low_disc & ip_A2020$est[,1] < up_disc)
print(names(which(outlier_disc == FALSE)))

Q_diff <- quantile(ip_A2020$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_A2020$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_A2020$est[,2] > low_diff & ip_A2020$est[,2] < up_diff)
print(names(which(outlier_diff == FALSE)))
```

```{r echo=FALSE}
u_A2020_2 <- select(u_A2020, -c('40'))
```

```{r echo=FALSE}
ip_A2020_2 <- est(resp=u_A2020_2, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_A2020_2$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r echo=FALSE}
plot(ip_A2020_2$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_A2020_2$est[,1], ip_A2020_2$est[,2], paste(rownames(ip_A2020_2$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```


### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_A2020$est)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve", cex.main = 0.75)
abline(h=0.5)
```


# ICC for selected items
```{r echo=FALSE}

#Set the threshold
#values.icc$x[26] = -2 - data for students of ability = -2
#values.icc$x[13] = -3.04 - data for students of ability = -3.04

# Selecting questions that half of the students of given ability get correct
values.icc_selected <- values.icc$f[, values.icc$f[26, ] > 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions')

counter <- 0
for (j in colnames(values.icc_selected)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected[,j], col = rainbow(ncol(values.icc_selected))[counter])
  
}
text(-4, values.icc_selected[1,], paste(colnames(values.icc_selected)), cex = 0.5)
abline(h = 0.5, v=-2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected))
```

#### Local independence {.tabset .tabset-fade}

##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_A2020 <- rowSums(u_A2020, na.rm = TRUE)
comp <- apply(u_A2020, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_A2020[comp,], var, na.rm=TRUE))
(sy <- var(y_A2020[comp]))
```

```{r echo=FALSE}
(37/36)*(1-sum(sj)/sy)
```

```{r echo=FALSE}
r_A2020 <- cor(u_A2020, use = "pairwise.complete.obs")
head(r_A2020)


reigen <- eigen(r_A2020)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)


#what does scree plot mean?
#since 12 of the items have eigenvalues>1, we only need 12 items to verify unidimensionality 
```



################################################################


### ES150 2020 Term B Grammar
```{r echo=FALSE}
B2020 <- read.csv("2020-ES150-B.csv",header = TRUE)
answersB2020 <- subset(B2020, select = c(11:83))
```

## Cleaning
```{r echo=FALSE}
for (col in colnames(answersB2020)){
  answersB2020[[col]][answersB2020[col] =="-"] <- NA
  answersB2020[[col]][answersB2020[col] > 0] <- 1
  answersB2020[[col]] <- as.numeric(answersB2020[[col]])
}

answersB2020 <- subset(answersB2020, select = c(1:5, 7:62, 64:73))
answersB2020 <- rename_with(answersB2020, ~ stringr::str_remove(., "..1.00"))
answersB2020 <- rename_with(answersB2020, ~ stringr::str_remove(., "Q.."))
```

#### 

<details>
<summary></summary>

```{r echo=FALSE}
summary(answersB2020)
```

#Boxplot
```{r echo=FALSE}
B2020$Grade_EB[B2020$Grade_EB == 0] <- NA
score <- na.omit(B2020$Grade_EB)
summary(score)
ggplot(B2020, aes(x = Grade_EB)) + geom_boxplot() + ggtitle("ES150 2020 Term B Grammar")
```

#Score distribution
```{r echo=FALSE}

ggplot(B2020, aes(x = Grade_EB)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2020 Term B Grammar")
```

# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(colnames(answersB2020))

avgData <- vector('numeric', 69L)
for (j in 1:69) avgData[j] <- sum(na.omit(answersB2020[,j]))/length(na.omit(answersB2020[,j]))

testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=8), legend.position = "none", plot.title = element_text(size=8)) + ggtitle("ES150 2020 Term B Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>


```{r echo=FALSE}
answersB2020 <- subset(answersB2020, select = -c(17, 42))

```

#### 2PLM

```{r echo=FALSE}
u_B2020 <- na.omit(answersB2020)
ip_B2020 <- est(resp=u_B2020, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_B2020$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```



#### Difficulty / Dscriminatory Power {.tabset .tabset-fade}

##### List

<details>
<summary></summary>
```{r}
ip_B2020$est
```

</details>

##### Plot
```{r echo=FALSE}
plot(ip_B2020$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2020$est[,1], ip_B2020$est[,2], paste(rownames(ip_B2020$est)), cex = 0.5)
```

## Removing outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_B2020$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_B2020$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_B2020$est[,1] > low_disc & ip_B2020$est[,1] < up_disc)

Q_diff <- quantile(ip_B2020$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_B2020$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_B2020$est[,2] > low_diff & ip_B2020$est[,2] < up_diff)

print(names(which(outlier_disc == FALSE)))
print(names(which(outlier_diff == FALSE)))

```

```{r echo=FALSE}
u_B2020_2 <- select(u_B2020, -c("17", "19", '20','21','22','29','39', "41", "42", "59"))
```

```{r echo=FALSE}
ip_B2020_2 <- est(resp = u_B2020_2, model = "2PL", engine = "ltm", a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")
```

```{r echo=FALSE}
plot(ip_B2020_2$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2020_2$est[,1], ip_B2020_2$est[,2], paste(rownames(ip_B2020_2$est)), cex = 0.5)
abline(v = 1, h = 0, lty = 2, lwd = 0.5)
```


### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_B2020_2$est)
ls(values.icc)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve")


```

#### Local independence {.tabset .tabset-fade}

##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_B2020 <- rowSums(u_B2020_2, na.rm = TRUE)
comp <- apply(u_B2020_2, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_B2020_2[comp,], var, na.rm=TRUE))
(sy <- var(y_B2020[comp]))
```

```{r echo=FALSE}
(37/36)*(1-sum(sj)/sy)
```

```{r echo=FALSE}
r_B2020 <- cor(u_B2020_2, use = "pairwise.complete.obs")
head(r_B2020)

reigen <- eigen(r_B2020)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)

```


################################################################


### ES150 2019 Term A Grammar
```{r}
A2019 <- read_excel("2019-ES150-A.xlsx")
key_A2019 <- A2019[1,4:42]
answersA2019 <- A2019[3:363, 4:42]
```

```{r}
answersA2019 <- rename_with(answersA2019, ~ stringr::str_remove(., "設問"))
```

```{r}
key_A2019 <- as.numeric(key_A2019)
answersA2019[answersA2019=='NA'] <- NA
for(j in 1:39) answersA2019[,j] <- as.numeric(unlist(answersA2019[,j]))
```

#### 記述統計 ES150

<details>
<summary></summary>

```{r echo=FALSE}
summary(answersA2019)
```

#Convert score into 100 scale
```{r echo=FALSE}
A2019_perfect <- sum(A2019[2,4:42])
  
A2019$得点[A2019$得点 == "-"] <- NA
A2019$得点 <- as.numeric(A2019$得点)
A2019$Grade_EA <- A2019$得点*100/A2019_perfect
```

#Boxplot
```{r echo=FALSE}
A2019$Grade_EA[A2019$Grade_EA == "-"] <- NA
score <- na.omit(A2019$Grade_EA)
A2019$得点 <- as.numeric(A2019$Grade_EA)
score <- as.numeric(score)
summary(score)
ggplot(A2019, aes(x = Grade_EA)) + geom_boxplot() + ggtitle("ES150 2019 Term A Grammar") + xlab('score')
```

#Score distribution
```{r echo=FALSE}

ggplot(A2019, aes(x = Grade_EA)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2019 Term A Grammar") + xlab('score')
```


```{r}
u_A2019 <- answersA2019
for(j in 1:361) u_A2019[j,] <- (key_A2019==answersA2019[j,])*1
```

# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(colnames(u_A2019))

avgData <- vector('numeric', 39L)
for (j in 1:39) avgData[j] <- sum(na.omit(u_A2019[,j]))/nrow(na.omit(u_A2019[,j]))

testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=8), legend.position = "none", plot.title = element_text(size=8)) + ggtitle("ES150 2019 Term A Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>


```{r echo=FALSE}
#u_A2019 <- na.omit(answersA2019)
ip_A2019 <- est(resp=u_A2019, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_A2019$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r}
ip_A2019$est
```

##### Plot
```{r echo=FALSE}
plot(ip_A2019$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_A2019$est[,1], ip_A2019$est[,2], paste(rownames(ip_A2019$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```

## Removing outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_A2019$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_A2019$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_A2019$est[,1] > low_disc & ip_A2019$est[,1] < up_disc)

Q_diff <- quantile(ip_A2019$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_A2019$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_A2019$est[,2] > low_diff & ip_A2019$est[,2] < up_diff)

print(names(which(outlier_disc == FALSE)))
print(names(which(outlier_diff == FALSE)))
```



### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_A2019$est)
ls(values.icc)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve")
abline(v=0, h=0.5, lwd=0.5)
```

# ICC for selected items
```{r echo=FALSE}

#Set the threshold
#values.icc$x[26] = -2 - data for students of ability = -2
#values.icc$x[13] = -3.04 - data for students of ability = -3.04

# Selecting questions that half of the students of given ability get correct
values.icc_selected <- values.icc$f[, values.icc$f[26, ] > 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions')

counter <- 0
for (j in colnames(values.icc_selected)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected[,j], col = rainbow(ncol(values.icc_selected))[counter])
  
}
text(-4, values.icc_selected[1,], paste(colnames(values.icc_selected)), cex = 0.5)
abline(h = 0.5, v=-2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected))
```

# ICC for selected items 2
```{r echo=FALSE}

#Set the threshold
#values.icc$x[76] = 2 - data for students of ability = 2

# Selecting questions that 60% of the students of given ability get correct
values.icc_selected_2 <- values.icc$f[, values.icc$f[76, ] < 0.6]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions 2')

counter <- 0
for (j in colnames(values.icc_selected_2)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected_2[,j], col = rainbow(ncol(values.icc_selected_2))[counter])
  
}
text(-4, values.icc_selected_2[1,], paste(colnames(values.icc_selected_2)), cex = 0.5)
abline(h = 0.6, v=2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected_2))
```


##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_A2019 <- rowSums(u_A2019, na.rm = TRUE)
comp <- apply(u_A2019, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_A2019[comp,], var, na.rm=TRUE))
(sy <- var(y_A2019[comp]))
```

```{r echo=FALSE}
r_A2019 <- cor(u_A2019, use = "pairwise.complete.obs")
head(r_A2019)

reigen <- eigen(r_A2019)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)
```

################################################################

### ES150 2019 Term B Grammar
```{r}
B2019 <- read.csv("2019-ES150-B.csv",header = TRUE, fileEncoding = "cp932")
key_B2019 <- B2019[1,4:78]
answersB2019 <- B2019[3:364, 4:78]
```

```{r}
answersB2019 <- rename_with(answersB2019, ~ stringr::str_remove(., "設問"))
```

```{r}
key_B2019 <- as.numeric(key_B2019)
answersB2019[answersB2019=='NA'] <- NA
for(j in 1:75) answersB2019[,j] <- as.numeric(unlist(answersB2019[,j]))
```

```{r}
u_B2019 <- answersB2019
for(j in 1:362) u_B2019[j,] <- (key_B2019==answersB2019[j,])*1
```

#### 記述統計 ES150

<details>
<summary></summary>

```{r echo=FALSE}
summary(u_B2019)
```

# calculate total score
```{r echo=FALSE}
total <- vector()
for(j in 1:362) total[j] <- sum(u_B2019[j,], na.rm=TRUE)
B2019$得点 <- c(c(NA, NA), total)
```

#Convert score into 100 scale
```{r echo=FALSE}
B2019_perfect <- length(B2019[2,4:78])
  
B2019$得点[B2019$得点 == "-"] <- NA
B2019$得点 <- as.numeric(B2019$得点)
B2019$Grade_EB <- B2019$得点*100/B2019_perfect
```


#Boxplot
```{r echo=FALSE}
B2019$Grade_EB[B2019$Grade_EB == "-"] <- NA
score <- na.omit(B2019$Grade_EB)
B2019$Grade_EB <- as.numeric(B2019$Grade_EB)
score <- as.numeric(score)
summary(score)
ggplot(B2019, aes(x = Grade_EB)) + geom_boxplot() + ggtitle("ES150 2019 Term B Grammar") + xlab('score')
```

#Score distribution
```{r echo=FALSE}

ggplot(B2019, aes(x = Grade_EB)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2019 Term B Grammar") + xlab('score')
```


# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(colnames(u_B2019))

avgData <- vector('numeric', 75L)
for (j in 1:75) avgData[j] <- sum(u_B2019[,j], na.rm=TRUE)/length(na.omit(u_B2019[,j]))

questionNumber <- factor(questionNumber, levels = sort(as.numeric(questionNumber)))
testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=8), legend.position = "none", plot.title = element_text(size=8)) + ggtitle("ES150 2019 Term B Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>


```{r echo=FALSE}
#u_A2018 <- na.omit(answersA2019)
ip_B2019 <- est(resp=u_B2019, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_B2019$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r}
ip_B2019$est
```


##### Plot
```{r echo=FALSE}
plot(ip_B2019$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2019$est[,1], ip_B2019$est[,2], paste(rownames(ip_B2019$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```

##### Remove outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_B2019$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_B2019$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_B2019$est[,1] > low_disc & ip_B2019$est[,1] < up_disc)

Q_diff <- quantile(ip_B2019$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_B2019$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_B2019$est[,2] > low_diff & ip_B2019$est[,2] < up_diff)

print(names(which(outlier_disc == FALSE)))
print(names(which(outlier_diff == FALSE)))
```

```{r echo=FALSE}
u_B2019_2 <- select(u_B2019, -c('4','6','7','18',"19", "20", "22",'44'))
```

```{r echo=FALSE}
#u_A2018 <- na.omit(answersA2019)
ip_B2019_2 <- est(resp=u_B2019_2, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_B2019_2$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r echo=FALSE}
plot(ip_B2019_2$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2019_2$est[,1], ip_B2019_2$est[,2], paste(rownames(ip_B2019_2$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```


### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_B2019$est)
ls(values.icc)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve")
abline(v = 0, h = 0.5, lwd = 0.5, lty=1)
```

# ICC for selected items
```{r echo=FALSE}

#Set the threshold
#values.icc$x[26] = -2 - data for students of ability = -2
#values.icc$x[13] = -3.04 - data for students of ability = -3.04

# Selecting questions that half of the students of given ability get correct
values.icc_selected <- values.icc$f[, values.icc$f[13, ] > 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions')

counter <- 0
for (j in colnames(values.icc_selected)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected[,j], col = rainbow(ncol(values.icc_selected))[counter])
  
}
text(-4, values.icc_selected[1,], paste(colnames(values.icc_selected)), cex = 0.5)
abline(h = 0.5, v=-3, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected))
```

# ICC for selected items 2
```{r echo=FALSE}

#Set the threshold
#values.icc$x[76] = 2 - data for students of ability = 2

# Selecting questions that half of the students of given ability get correct
values.icc_selected_2 <- values.icc$f[, values.icc$f[76, ] < 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions 2')

counter <- 0
for (j in colnames(values.icc_selected_2)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected_2[,j], col = rainbow(ncol(values.icc_selected_2))[counter])
  
}
text(-4, values.icc_selected_2[1,], paste(colnames(values.icc_selected_2)), cex = 0.5)
abline(h = 0.5, v=2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected_2))
```


##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_B2019 <- rowSums(u_B2019, na.rm = TRUE)
comp <- apply(u_B2019, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_B2019[comp,], var, na.rm=TRUE))
(sy <- var(y_B2019[comp]))
```

```{r echo=FALSE}
r_B2019 <- cor(u_B2019, use = "pairwise.complete.obs")
head(r_B2019)

reigen <- eigen(r_B2018)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)
```


################################################################

### ES150 2018 Term A Grammar
```{r}
A2018 <- read_excel("2018-ES150-A.xlsx")
key_A2018 <- A2018[1,4:41]
answersA2018 <- A2018[3:382, 4:41]
```

```{r}
answersA2018 <- rename_with(answersA2018, ~ stringr::str_remove(., "設問"))
```

```{r}
key_A2018 <- as.numeric(key_A2018)
answersA2018[answersA2018=='NA'] <- NA
for(j in 1:38) answersA2018[,j] <- as.numeric(unlist(answersA2018[,j]))
```

```{r}
u_A2018 <- answersA2018
for(j in 1:380) u_A2018[j,] <- (key_A2018==answersA2018[j,])*1
```

#### 記述統計 ES150

<details>
<summary></summary>

```{r echo=FALSE}
summary(u_A2018)
```
# calculate total score
```{r echo=FALSE}
total <- vector()
for(j in 1:380) total[j] <- sum(u_A2018[j,], na.rm=TRUE)
A2018$得点 <- c(c(NA, NA), total)
```

#Convert score into 100 scale
```{r echo=FALSE}
A2018_perfect <- length(A2018[2,4:41])
  
A2018$得点[A2018$得点 == "-"] <- NA
A2018$得点 <- as.numeric(A2018$得点)
A2018$Grade_EA <- A2018$得点*100/A2018_perfect
```


#Boxplot
```{r echo=FALSE}
A2018$Grade_EA[A2018$Grade_EA == "-"] <- NA
score <- na.omit(A2018$Grade_EA)
A2018$Grade_EA <- as.numeric(A2018$Grade_EA)
score <- as.numeric(score)
summary(score)
ggplot(A2018, aes(x = Grade_EA)) + geom_boxplot() + ggtitle("ES150 2018 Term A Grammar") + xlab('score')
```

#Score distribution
```{r echo=FALSE}

ggplot(A2018, aes(x = Grade_EA)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2018 Term A Grammar") + xlab('score')
```


# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(colnames(u_A2018))

avgData <- vector('numeric', 38L)
for (j in 1:38) avgData[j] <- sum(na.omit(u_A2018[,j]))/nrow(na.omit(u_A2018[,j]))

testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=8), legend.position = "none", plot.title = element_text(size=8)) + ggtitle("ES150 2018 Term A Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>


```{r echo=FALSE}
#u_A2018 <- na.omit(answersA2019)
ip_A2018 <- est(resp=u_A2018, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_A2018$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r}
ip_A2018$est
```


##### Plot
```{r echo=FALSE}
plot(ip_A2018$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_A2018$est[,1], ip_A2018$est[,2], paste(rownames(ip_A2018$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```

## Removing outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_A2018$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_A2018$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_A2018$est[,1] > low_disc & ip_A2018$est[,1] < up_disc)

Q_diff <- quantile(ip_A2018$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_A2018$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_A2018$est[,2] > low_diff & ip_A2018$est[,2] < up_diff)

print(names(which(outlier_disc == FALSE)))
print(names(which(outlier_diff == FALSE)))
```


### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_A2018$est)
ls(values.icc)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve")
abline(v = 0, h = 0.5, lwd = 0.5, lty=1)
```

# ICC for selected items
```{r echo=FALSE}

#Set the threshold
#values.icc$x[26] = -2 - data for students of ability = -2
#values.icc$x[13] = -3.04 - data for students of ability = -3.04

# Selecting questions that half of the students of given ability get correct
values.icc_selected <- values.icc$f[, values.icc$f[26, ] > 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions')

counter <- 0
for (j in colnames(values.icc_selected)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected[,j], col = rainbow(ncol(values.icc_selected))[counter])
  
}
text(-4, values.icc_selected[1,], paste(colnames(values.icc_selected)), cex = 0.5)
abline(h = 0.5, v=-2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected))
```

##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_A2018 <- rowSums(u_A2018, na.rm = TRUE)
comp <- apply(u_A2018, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_A2018[comp,], var, na.rm=TRUE))
(sy <- var(y_A2018[comp]))
```

```{r echo=FALSE}
r_A2018 <- cor(u_A2018, use = "pairwise.complete.obs")
head(r_A2018)

reigen <- eigen(r_A2018)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)
```


##################################################


### ES150 2018 Term B Grammar
```{r}
B2018 <- read_excel("2018-ES150-B.xlsx")
key_B2018 <- B2018[1,4:82]
answersB2018 <- B2018[3:362, 4:82]
```

```{r}
answersB2018 <- rename_with(answersB2018, ~ stringr::str_remove(., "設問"))
```

```{r}
key_B2018 <- as.numeric(key_B2018)
answersB2018[answersB2018=='NA'] <- NA
for(j in 1:79) answersB2018[,j] <- as.numeric(unlist(answersB2018[,j]))
```

```{r}
u_B2018 <- answersB2018
for(j in 1:360) u_B2018[j,] <- (key_B2018==answersB2018[j,])*1
```

#### 記述統計 ES150

<details>
<summary></summary>

```{r echo=FALSE}
summary(u_B2018)
```

#Convert score into 100 scale
```{r echo=FALSE}
B2018_perfect <- sum(B2018[2,4:82])
  
B2018$得点[B2018$得点 == "-"] <- NA
B2018$得点 <- as.numeric(B2018$得点)
B2018$Grade_EB <- B2018$得点*100/B2018_perfect
```


#Boxplot
```{r echo=FALSE}
B2018$Grade_EB[B2018$Grade_EB == "-"] <- NA
score <- na.omit(B2018$Grade_EB)
B2018$Grade_EB <- as.numeric(B2018$Grade_EB)
score <- as.numeric(score)
summary(score)
ggplot(B2018, aes(x = Grade_EB)) + geom_boxplot() + ggtitle("ES150 2018 Term B Grammar") + xlab('score')
```

#Score distribution
```{r echo=FALSE}

ggplot(B2018, aes(x = Grade_EB)) + geom_histogram(binwidth = 5, colour="black", fill="white") + geom_density()+ ggtitle("ES150 2018 Term B Grammar") + xlab('score')
```


# Propotion of correct answers per question
```{r echo=FALSE}
questionNumber <- as.character(colnames(u_B2018))


avgData <- vector('numeric', 79L)
for (j in 1:79) avgData[j] <- sum(na.omit(u_B2018[,j]))/nrow(na.omit(u_B2018[,j]))

questionNumber <- factor(questionNumber, levels = sort(as.numeric(questionNumber)))
testData <- data.frame(questionNumber, avgData)

summary(testData$avgData*100)

ggplot(testData, aes(x = questionNumber, y = avgData, fill = avgData)) + geom_bar(stat = 'identity') + xlab("Question Number") + ylab("Propotion of correct answers") + theme(axis.text=element_text(size=6), axis.title=element_text(size=8), legend.position = "none", plot.title = element_text(size=8)) + ggtitle("ES150 2018 Term B Grammar")
```

```{r echo=FALSE}
summary(avgData)
```

</details>

```{r echo=FALSE}
#u_B2018 <- na.omit(answersB2018)
ip_B2018 <- est(resp=u_B2018, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_B2018$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r}
ip_B2018$est
```


##### Plot
```{r echo=FALSE}
plot(ip_B2018$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2018$est[,1], ip_B2018$est[,2], paste(rownames(ip_B2018$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)
```

## Removing outliers
## Removing outliers
```{r echo=FALSE}
Q_disc <- quantile(ip_B2018$est[,1], probs=c(.25, .75), na.rm = FALSE)
iqr_disc <- IQR(ip_B2018$est[,1])
up_disc <-  Q_disc[2]+1.5*iqr_disc  
low_disc <- Q_disc[1]-1.5*iqr_disc
outlier_disc <- (ip_B2018$est[,1] > low_disc & ip_B2018$est[,1] < up_disc)

Q_diff <- quantile(ip_B2018$est[,2], probs=c(.25, .75), na.rm = FALSE)
iqr_diff <- IQR(ip_B2018$est[,2])
up_diff <-  Q_diff[2]+1.5*iqr_diff 
low_diff <- Q_diff[1]-1.5*iqr_diff
outlier_diff <- (ip_B2018$est[,2] > low_diff & ip_B2018$est[,2] < up_diff)

print(names(which(outlier_disc == FALSE)))
print(names(which(outlier_diff == FALSE)))
```

```{r echo=FALSE}
u_B2018_2 <- select(u_B2018, -c("15", '27','29','44','66','76'))
```

```{r echo=FALSE}
ip_B2018_2 <- est(resp=u_B2018_2, model = "2PL", engine = "ltm",a.prior = FALSE, b.prior = FALSE, c.prior = FALSE, run.name = "L2_2PL")

kable(summary(ip_B2018_2$est)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r echo=FALSE}
plot(ip_B2018_2$est[,1:2], type = "n", xlab = "Discriminatory power", ylab = "Difficulity")
text(ip_B2018_2$est[,1], ip_B2018_2$est[,2], paste(rownames(ip_B2018_2$est)), cex = 0.5)
abline(v = 1, h = 0, lwd = 0.5, lty=2)

mean(ip_B2018_2$est[,1])
mean(ip_B2018_2$est[,2])
```


### Item Characteristic Curve
```{r echo=FALSE}
values.icc <- irf(ip_B2018$est)
ls(values.icc)
plot(values.icc, label=TRUE,co=NA, main = "Item Characteristic Curve")
abline(v = 0, h = 0.5, lwd = 0.5, lty=1)
```

# ICC for selected items
```{r echo=FALSE}

#Set the threshold
#values.icc$x[26] = -2 - data for students of ability = -2
#values.icc$x[13] = -3.04 - data for students of ability = -3.04

# Selecting questions that half of the students of given ability get correct
values.icc_selected <- values.icc$f[, values.icc$f[13, ] > 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions')

counter <- 0
for (j in colnames(values.icc_selected)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected[,j], col = rainbow(ncol(values.icc_selected))[counter])
  
}
text(-4, values.icc_selected[1,], paste(colnames(values.icc_selected)), cex = 0.5)
abline(h = 0.5, v=-3, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected))
```

# ICC for selected items 2
```{r echo=FALSE}

#Set the threshold
#values.icc$x[76] = 2 - data for students of ability = 2


# Selecting questions that half of the students of given ability get correct
values.icc_selected_2 <- values.icc$f[, values.icc$f[76, ] < 0.5]
plot(values.icc$x, type="n", ylab = "Probability of a correct response", xlab = "Ability", xlim = c(-4,4), ylim = c(0.0, 1.0), main = 'ICC for selected questions 2')

counter <- 0
for (j in colnames(values.icc_selected_2)){
  counter <- counter + 1
  lines(values.icc$x,values.icc_selected_2[,j], col = rainbow(ncol(values.icc_selected_2))[counter])
  
}
text(-4, values.icc_selected_2[1,], paste(colnames(values.icc_selected_2)), cex = 0.5)
abline(h = 0.5, v=2, lty=2, lwd=0.5)

# These are not good questions since students with low ability can still get them correct
print(colnames(values.icc_selected_2))
```

##### Correlation coefficient

<details>
<summary></summary>
```{r echo=FALSE}
y_B2018 <- rowSums(u_B2018, na.rm = TRUE)
comp <- apply(u_B2018, 1, function(x) all(!is.na(x)))
(sj <- sapply(u_B2018[comp,], var, na.rm=TRUE))
(sy <- var(y_B2018[comp]))
```

```{r echo=FALSE}
r_B2018 <- cor(u_B2018, use = "pairwise.complete.obs")
head(r_B2018)

reigen <- eigen(r_B2018)
reigen$values
```

</details>


##### Scree Plot
```{r}
plot(reigen$values, type = "o", ylab = "Eigenvalues", main = "Scree Plot", cex=0.5)
abline(h=1)
```

#####################################################################

# Compare each year
```{r}
A2020_box <- ggplot(A2020, aes(y = Grade_EA)) + geom_boxplot() + theme(axis.title.y = element_blank()) + ylim(0, 100)
A2019_box <- ggplot(A2019, aes(y = Grade_EA)) + geom_boxplot() + theme(axis.title.y = element_blank()) + ylim(0, 100)
A2018_box <- ggplot(A2018, aes(y = Grade_EA)) + geom_boxplot()+ theme(axis.title.y = element_blank()) + ylim(0, 100)
ggarrange(A2018_box, A2019_box, A2020_box, labels = c("2018", "2019", "2020"), nrow = 1, ncol = 3, font.label = list(size = 12, color = "black", face = 'plain'), hjust = -1.5)
```

```{r}
B2020_box <- ggplot(B2020, aes(y = Grade_EB)) + geom_boxplot() + theme(axis.title.y = element_blank()) + ylim(0, 100)
B2019_box <- ggplot(B2019, aes(y = Grade_EB)) + geom_boxplot() + theme(axis.title.y = element_blank()) + ylim(0, 100)
B2018_box <- ggplot(B2018, aes(y = Grade_EB)) + geom_boxplot()+ theme(axis.title.y = element_blank()) + ylim(0, 100)
ggarrange(B2018_box, B2019_box, B2020_box, labels = c("2018", "2019", "2020"), nrow = 1, ncol = 3, font.label = list(size = 12, color = "black", face = 'plain'), hjust = -1.5)
```